### 2019-10-07 paper/results.tex
Flux added, text ofsusbsection added

\begin{table} % [!ht]
	\centering
	\caption{Comparison between the two feed mechanisms for the five different types of initial fuel.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l s s s s s }  %{\textwidth}
		\hline
		\backslashbox{Feed\\ mechanism}{Initial\\ fuel}& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		Thorium feed mechanism&Not work&Not work&Not work&Not work& Work\\
		Non-thorium feed mechanism &Not work&Not work&Work well with positive net production of $^{233}$U &Work for $40$ $years$ with net production of $^{233}$U = zero & Not examine (supercritical reactor)\\
		\hline
	\end{tabularx}
	\label{tab:table7}
\end{table}

>>>>

\begin{table} % [!ht]
	\centering
	\caption{Comparison between the two feed mechanisms for the five different types of initial fuel.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l s s s s s }  %{\textwidth}
		\hline
		\backslashbox{Feed\\ mechanism}{Initial\\ fuel}& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		Thorium feed mechanism&Not work&Not work&Not work&Not work& Work\\
		Non-thorium feed mechanism &Not work&Not work&Work well with positive net production of $^{233}$U &Work for $40$ $years$ with net production of $^{233}$U = zero & Not examine (supercritical reactor)\\
		\hline
	\end{tabularx}
	\label{tab:table7}
\end{table}
\FloatBarrier

\subsection{Neutron flux}
Figures~\ref{fig:fast_flux}, \ref{fig:thermal_flux} show the radial 
distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
(energy range between 10$^{-5}$ eV and 0.625 eV) neutron flux for three 
different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
plutonium, TRU) at startup and at equilibrium (after $\approx 30$ years of 
operation). Actinides evolution and poisonous fission products accumulation 
for various initial fissile compositions demonstrated different effect on the 
SD-TMSR neutronics performance. For the Th/$^{233}$U, thermal neutron flux is 
suppressed at the equilibrium state because fissile $^{233}$U in the core is 
being substituted with heavier fissile actinides: $^{235}$U, $^{239}$Pu, and 
$^{241}$Pu which is in a good agreement with results the literature 
\cite{rykhlevskii2019modeling, ashraf2019whole_core}.
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_fast_flux_init_vs_eq.png} 
	\caption{Radial fast neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the fast flux 
		confidence interval $\pm\sigma<2.5$\% for all cases).}
	\label{fig:fast_flux}
\end{figure}

Opposite observation has been made for reactor-grade Pu and TRU cases. For 
these cases, thermal neutron flux is increasing during operation while fast 
neutron flux is decreasing. The fissile Pu (generates relatively hard 
spectrum) from initial fuel salt composition is gradually substituted with the 
$^{233}$U (generates relatively soft spectrum), produced from the fertile 
$^{232}$Th. During reactor operation, the $^{233}$U becomes primary fissile 
isotope which leads to the neutron spectrum softening of the reactor. 
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
	\caption{Radial thermal neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium for initial and 
		equilibrium fuel salt composition (the thermal flux confidence 
		interval 
		$\pm\sigma<1.6$\% for all cases).}
	\label{fig:thermal_flux}
\end{figure}

Notably, more changes in thermal neutron flux shape and magnitude for  
$^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for Pu reactor-grade and TRU case, large 
changes were observed for thermal neutron flux in the outer core zone and 
reflector. Additionally, Figure~\ref{fig:thermal_flux} shows relatively large 
changes in thermal flux leakage from the core for Pu case. Overall, the 
SD-TMSR core design was optimized for $^{233}$U fissile isotope 
\cite{li_optimization_2018}, hence, the core geometry (e.g., fuel channels  
lattice pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.

\subsection{Temperature coefficient of reactivity}
To determine 
the temperature coefficients, the cross-section temperatures for the fuel and 
moderator were changed from 900 K to 1000 K. This study considered three 
different cases:
\begin{enumerate}
	\item Fuel salt temperature rising from 900 K to 1000 K.
	\item Graphite temperature rising from 900 K to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.255\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ \\ 
		Fuel density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ \hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Six Factor analysis}
The effective multiplication factor can be expressed using the following 
formula:
\begin{align*}
k_{eff} = k_{inf} P_f  P_t = \eta \epsilon p f P_f P_t
\end{align*}

Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
equilibrium 
fuel salt composition. Using SERPENT-2 built-in online reprocessing 
capabilities all six 
factors and their statistical uncertainties have been calculated at the 
beginning of 
operation and after 20 years of operation. The fast and thermal non-leakage 
probabilities 
and the thermal utilization factor (f)
remain constant regardless of neutron spectrum hardening during operation. In 
contrast, the 
neutron reproduction factor ($\eta$), resonance escape probability ($p$), and 
fast fission 
factor ($\epsilon$) differ notably between initial and equilibrium state. The 
neutron 
spectrum is soft at the beginning of reactor life (Figure~\ref{fig:spectrum}), 
but 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} %[hb!]
	\caption{Six factors for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X | X X | X X } \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
		material} \\ 
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\
		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.57 & 1.31 \\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
	    p       & 0.54 & 0.43 & 0.26 & 1.60 & 0.17 & 0.15 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
        P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
neutron 
spectrum hardening causes the fast fission factor to grow throughout the 
core's lifetime. Conversely, 
the resonance escape probability decreases during reactor operation. The 
neutron reproduction factor increases during reactor operation due to 
accumulation of fissile plutonium 
isotopes, which produce more neutrons per fission ($\nu$). This six factors' 
evolution agrees with 
previously determined evolution parameters for a similar single-fluid 
double-zone \gls{MSBR} \cite{rykhlevskii2019modeling, park_whole_2015}.
